\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-11-11 icra-2021.tex
changed a par in intro, this reads better

The proposed algorithm contributes to the UAV mission planning problem as follows. The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters: the Quality of Service (QoS) computations are relative to the tasks. The trajectory-explicit equations (TEEs) adjustments are relative to the path. The computations specify a given task's computational level. The adjustments are a way to alter the TEE. The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences. The goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain. 
The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature. It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory. The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. 
In the remainder of the paper, we adopt the following notation. We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.

>>>>

Our goal is to complete the mission with the highest possible computations and adjustments as the UAV flies and its batteries drain. 
The algorithm plans both tasks and trajectory unlike most of the past planning algorithms literature. It guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to the planned trajectory. The vector field for planning is widely discussed in the literature~\cite{lindemann2005smoothly,gonccalves2010vector,panagou2014motion,zhou2014vector,kapitanyuk2017guiding}. 
The user specifies an initial mission plan--the trajectory and the tasks--along with an energy budget and some parameters: the Quality of Service (QoS) computations are relative to the tasks. The trajectory-explicit equations (TEEs) adjustments are relative to the path. The computations specify a given task's computational level. The adjustments are a way to alter the TEE. The algorithm replans the initial mission plan as the energy budget changes due to atmospheric interferences.
In the remainder of the paper, we adopt the following notation. We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, we refer to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and we refer to the current trajectory as TEE.
